CFF GCT Study

### 2025-07-14 Christine Chan/CFF GCT Study/cff_gct_analysis.qmd
cleaned up EnVision folder
new GCT figures

```{r}
#| label: fig-boxplot
#| fig-cap: Boxplot of OGTT glucose values by diabetes status
# The code below is a total mess because Larry keeps sending requests -
# clean up later

@@

  pivot_longer(c(`OGTT 0 min`, `OGTT 60 min`, `OGTT 120 min`),

@@

  levels = c("OGTT 0 min", "OGTT 60 min", "OGTT 120 min"),
  labels = c("Fasting", "OGTT-1hG", "OGTT-2hG")

@@

  scale_fill_manual(values = RColorBrewer::brewer.pal(3, "Paired")) +

@@

dotplot <- ggplot(df, aes(x = Diagnosis, y = `GCT 60 min plasma`)) +
  ylab("GCTpl (mg/dL)") +
  theme_bw()
  pivot_longer(c(`OGTT 0 min`, `OGTT 60 min`, `OGTT 120 min`, `GCT 60 min plasma`),
  levels = c("OGTT 0 min", "OGTT 60 min", "OGTT 120 min", "GCT 60 min plasma"),
  labels = c("Fasting", "OGTT-1hG", "OGTT-2hG", "GCTpl")
  scale_fill_manual(values = RColorBrewer::brewer.pal(4, "Set2")) +
# GCTpl, RCG, HbA1c, OGTT1hr

@@

      `GCT 60 min plasma`, `GCT 0 min capillary`, HbA1c,
      `OGTT 60 min`

@@

box_p1 <- ggplot(
  aes(x = Diabetes, y = Value, fill = Diabetes)
  geom_hline(yintercept = 146.5, linetype = "dashed") +
  ylab("mg/dL") +
box_p2 <- ggplot(
  aes(x = Diabetes, y = Value, fill = Diabetes)
  geom_hline(yintercept = 98.5, linetype = "dashed") +
box_p3 <- ggplot(
  aes(x = Diabetes, y = Value, fill = Diabetes)
  geom_hline(yintercept = 5.45, linetype = "dashed") +
box_p4 <- ggplot(
  plot_df[plot_df$Measure == "OGTT 60 min", ],
  aes(x = Diabetes, y = Value, fill = Diabetes)
  geom_hline(yintercept = 228.5, linetype = "dashed") +
  ggtitle("OGTT 60 min") +
box_p <- box_p1 + box_p2 + box_p3 + box_p4
ggsave("./Christine Chan/CFF GCT Study/Dissemination/Figures/boxplot2.png",

@@

box_p1 <- ggplot(

@@

  geom_hline(yintercept = 146.5, linetype = "dashed", size = 1) +

@@

@@

  scale_colour_manual(values = RColorBrewer::brewer.pal(3, "Set2")) +

@@

box_p2 <- ggplot(

@@

  geom_hline(yintercept = 98.5, linetype = "dashed", size = 1) +

@@

box_p3 <- ggplot(

@@

box_p4 <- ggplot(
  plot_df[plot_df$Measure == "OGTT 60 min", ],
  geom_hline(yintercept = 228.5, linetype = "dashed", size = 1) +
  ggtitle("OGTT 1hPG") +
  scale_colour_manual(values = RColorBrewer::brewer.pal(3, "Set2")) +
box_p <- box_p1 + box_p2 + box_p4 + box_p3 + plot_layout(ncol = 4)

>>>>

```{r}
#| warning: false
# The code below is a total mess because Larry keeps sending requests -
# clean up later
plot_df <- df %>%
  pivot_longer(c(`OGTT 0 min`, `OGTT 60 min`, `OGTT 120 min`),
    names_to = "OGTT Timepoint", values_to = "Glucose"
  )
plot_df$`OGTT Timepoint` <- factor(plot_df$`OGTT Timepoint`,
  levels = c("OGTT 0 min", "OGTT 60 min", "OGTT 120 min"),
  labels = c("Fasting", "OGTT-1hG", "OGTT-2hG")
)
box_p <- ggplot(
  plot_df,
  aes(x = `OGTT Timepoint`, y = Glucose, fill = `OGTT Timepoint`)
) +
  geom_boxplot() +
  ylab("Glucose (mg/dL)") +
  scale_y_continuous(breaks = c(100, 140, 200, 300)) +
  scale_fill_manual(values = RColorBrewer::brewer.pal(3, "Paired")) +
  facet_wrap(~Diabetes) +
  theme_bw(base_size = 20) +
  theme(
    legend.position = "none",
    axis.text.x = element_text(angle = 45, hjust = 1),
    axis.title.x = element_blank()
  )
box_p
ggsave("./Christine Chan/CFF GCT Study/Dissemination/Figures/boxplot.png",
  box_p,
  device = "png"
)
# Dotplot
dotplot <- ggplot(df, aes(x = Diagnosis, y = `GCT 60 min plasma`)) +
  geom_point() +
  geom_hline(yintercept = 140, linetype = "dashed") +
  geom_hline(yintercept = 150, linetype = "dashed") +
  geom_hline(yintercept = 160, linetype = "dashed") +
  geom_hline(yintercept = 147, linetype = "dashed", size = 1) +
  ylab("GCTpl (mg/dL)") +
  theme_bw() +
  scale_y_continuous(breaks = c(100, 140, 147, 150, 160))

@@

      `OGTT 0 min`, `OGTT 120 min`, `GCT 0 min plasma`, `GCT 60 min plasma`,
      `GCT 60 min capillary`

@@

  levels = c(
    "OGTT 0 min", "OGTT 120 min", "GCT 0 min plasma", "GCT 60 min plasma",
    "GCT 60 min capillary"
  labels = c("Fasting", "OGTT-2hG", "RPG", "GCTpl", "GCTcap")

@@

  scale_fill_manual(values = RColorBrewer::brewer.pal(5, "Dark2")) +

@@

# RPG, GCTpl, RCG, HbA1c, OGTT1hr

@@

      `GCT 0 min plasma`, `GCT 60 min plasma`, `GCT 0 min capillary`,
      `GCT 60 min capillary`, HbA1c

@@

@@

dot_p1 <- ggplot(
  plot_df[plot_df$Measure == "GCT 0 min plasma", ],

@@

  geom_hline(yintercept = 91.5, linetype = "dashed", size = 1) +

@@

  ggtitle("RPG") +

@@

  scale_colour_manual(values = c("#00ADB5", "#F4CE14", "#222831")) +

@@

dot_p2 <- ggplot(

@@

  geom_hline(yintercept = 140.5, linetype = "dashed", size = 1) +

@@

dot_p3 <- ggplot(
  geom_hline(yintercept = 97.5, linetype = "dashed", size = 1) +
  scale_colour_manual(values = c("#00ADB5", "#F4CE14", "#222831")) +
dot_p4 <- ggplot(
  plot_df[plot_df$Measure == "GCT 60 min capillary", ],
  geom_hline(yintercept = 161.5, linetype = "dashed", size = 1) +
  ggtitle("GCTcap") +
  scale_colour_manual(values = c("#00ADB5", "#F4CE14", "#222831")) +
dot_p5 <- ggplot(

@@

dot_p <- dot_p1 + dot_p2 + dot_p3 + dot_p4 + dot_p5 + plot_layout(ncol = 5)
